An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-01-07 answer-to-reviewers/answer-to-reviewers.tex

\textbf{Cross references are incorrect. Algorithm 1 is cited as algorithm 11 in the manuscript.
Please check latex file of your manuscript.}

~\\
$\rightarrow$ Thank you for pointing out. Corrections were made.
~\\

~\\
\textbf{Eq. (4) is proposed in this paper.
"Gradient flow" like evolution of digital planar boundary which minimises energy of eq. (4).
For the understanding of the differences and similarity between definitions for eqs. (3) and (4),
step-by-step graphical descriptions of definitions and equations in section 2 are preferable.}

~\\
$\rightarrow$ We are not quite sure what the reviewer is asking here. Optimisation of the Elastica (equation (3)) in the
continuous domain is itself a complex problem that has been studied by Mumford and others. In section 3 we conduct a
minimization of equation (4) only, which is the discrete equivalent of equation (3). We hope that the new explanations
and figures in section 3 answer the reviewer's concerns.
~\\

@@

\textbf{Second paragraph insection3 describes the main mathematical idea for curve evolution in digital space. In the process selection of the local neighbourhood is essential in your proposal. The graphical explanation is preferable. These descriptions provide the necessity of the distance transform in the local operations.}

~\\
$\rightarrow$ New figures were included in section 3. We hope they will help clarify this point.
~\\

\textbf{In algorithm 1 (11) $X^\ast$ s.t .$\hat{E}(X)< E(X^ast)$ is searched, how can you mathematically guarantee $\hat{E}(X)< E(X^\ast)$? Please describe why such $X^{\ast}$ exists.}

~\\
$\rightarrow$ It may not exist! If the neighborhood is exhausted and such X* is not found, the algorithm simply stops. Specifically, the shapes S(i) and S(i-1) will be the same, hence delta will be zero and there will be no next iteration.
~\\

### 2020-01-07 Revision/Biographies/biographies.tex
Add bio jol

\paragraph{Jacques-Olivier Lachaud}
A splendid researcher, great mentor and fast friend.

>>>>

\paragraph{Jacques-Olivier Lachaud}
Jacques-Olivier Lachaud graduated from ENSIMAG engineering school in
Computer Science in 1994 and received a Ph.D. degree in computer
science from Joseph Fourier University (Grenoble, France) in 1998 and
the Habilitation from University Bordeaux 1 in 2006. He is now a
Professor of Computer Science at the University Savoie Mont Blanc
(Chambéry, France) and works in the laboratory of mathematics
(LAMA). His research interests are in image analysis and geometry
processing, more specifically deformable models, energy-minimizing
techniques, digital geometry and topology. He has written over 100
articles in international journals and conferences on these topics.
%% JO :-D A splendid researcher, great mentor and fast friend.
